Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
passive to active

As described earlier, Moltres runs naturally in parallel. To test its
performance, a scaling study was conducted using a typical 2D axisymmetric input
file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
time follows closely to the ideal; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means more ``older'' information is used in the solution process,
which leads to slower convergence in terms of iterations \cite{satish_balay_petsc_2015}.

>>>>

As described earlier, Moltres runs naturally in parallel. To test its
performance, a scaling study was conducted using a typical 2D axisymmetric input
file. \Cref{fig:scaling_study} shows Moltres's performance. The solution
time follows the ideal closely; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means the solution process uses more ``older'' information, 
which leads to slower convergence in terms of iterations 
\cite{satish_balay_petsc_2015}.
